The Tail Risk Premium - Extension of Lottery Preference Premium

### 2025-03-18 paper.qmd
Added Updates To Formatting

### Monthly Returns

@@

monthly_total_return()

@@

#### Monthly Return Histogram
```{python}
from visuals import monthly_hist

#### Annual Returns (Value of $100k Invested)
```{python}
from visuals import annual_ret
annual_ret()

@@

#### V2 Alpha

@@

#### Equal Weighted Portfolios (Baseline vs Strategy-Extension)

>>>>

### Four Portfolio Metrics

Four portfolio's were constructed under the assumption of equal weighting dynamics. V1 portfolios are comprised of 100 companies and screen through IVOL. V2 portfolios describe our teams extension of the V1 sceen, which utilizes skew to screen for 30 companies in each portfolio.

#### Monthly Returns

```{python}
from visuals import monthly_ret

monthly_ret()

#### Monthly Return Histogram

```{python}
from visuals import monthly_hist

#### Cumalitve Monthly Returns (Value of $1 Invested)

@@

monthly_total_return()
```

#### Annual Returns (Value of $1 Invested)
```{python}
from visuals import annual_ret
annual_ret()

@@

### Screening Variables

The screening variables are broken into four categories, under the asumption of a three year lookback period. Base Long utilizes the lowest 100 IVOL from the dataset each year. In contrast, the Base Short utilizes the highest 100 IVOL from the dataset.

@@

### Portfolio Positions
The portfolios are equal weighted. This provides an accurate representation of both the V1 and V2 screening effectiveness.

#### Equal Weighted Portfolios (Baseline vs Strategy-Extension) Cumalitve Returns (Value of $1 Invested)

#### V2 Strategy Alpha Relative To V1 Baseline

@@
